The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/method-of-moments.tex
Redid images. Extensively.

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../images/restriction-least-n.png}
  \caption{Least possible $n$, given a fixed $p$}
  \label{fig:sn-restriction-least-n}
\end{figure}

@@

Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
interval grows quickly as $n$ increases, and for sufficiently large $n$, it
becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
0.99029)$; when $n=500$, it is (0.00199, 0.99801).

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{../images/restriction-p-range.png}
  \caption{Range of possible $p$, given a fixed $n$}
  \label{fig:sn-restriction-p-range}
\end{figure}

>>>>

@@

Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:graphs} shows this
range as a function of $n$, this interval grows quickly as $n$ increases, and
for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
0.99801).

### 2011-01-22 project/paper/output.tex
Cleaning up a little bit.
Few more tweaks.
Redid images. Extensively.

%\footnotetext{A random variable $X$ follows the normal distribution with mean
%$\mu$ and variance $\sigma^2$ if it has the pdf
%
%\begin{equation*}
%  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
%\end{equation*}
%
%for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
%\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
%
%$N(0,1)$ is an important special case known as the standard normal (denoted
%$Z$) and has pdf
%
%\begin{equation*}
%  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
%\end{equation*}
%
%and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
%
%Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

@@

The skew-normal was first introduced by \citet{o'hagan} and was most notably
further developed by \citet{azzalini-1985}. Some of its other basic properties,
given by \citet{pewsey}, are

@@

\begin{proof}
  The standard normal pdf is an even function: $\phi(-x) =
  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^t
  \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
  $\infty$. Thus,

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
  \caption{MABS as a function of p}
  \label{fig:mabs-fixed-n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../images/mabs-fixed-p.png}
  \caption{MABS as a function of n}
  \label{fig:mabs-fixed-p}
\end{figure}

@@

\appendix
\section{Calculating a Skew-Normal Approximation}
\label{app:calc-sn-approx}

>>>>

@@

The skew-normal was first introduced by \citet{o'hagan} and was most notably
developed by \citet{azzalini-1985}. Some of its other basic properties, given
by \citet{pewsey}, are

@@

\begin{proof}
  The standard normal pdf is an even function: $\phi(-x) =
  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^x
  \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
  $\infty$. Thus,

@@

\appendix
\section{Figures}
\label{app:figures}

\begin{figure}[h]
  \centering
  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.76\textwidth]{../images/restriction-least-n.png}}
  \\ \vspace{5mm}
  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.76\textwidth]{../images/restriction-p-range.png}}
  \caption{Restrictions on $n$ and $p$ necessary to obtain $\lambda$}
  \label{fig:sn-restriction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n.png}
  \caption{MABS as a function of p}
  \label{fig:mabs-fixed-n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p.png}
  \caption{MABS as a function of n}
  \label{fig:mabs-fixed-p}
\end{figure}

%\begin{figure}
%  \centering
%  \subfloat{\label{fig:mabs-n25}\includegraphics[width=0.8\textwidth]{../images/mabs-n25.png}}                
%  \\ \vspace{5mm}
%  \subfloat{\label{fig:mabs-n100}\includegraphics[width=0.8\textwidth]{../images/mabs-n100.png}}
%  \caption{MABS as a function of p}
%  \label{fig:mabs-fixed-n}
%\end{figure}
%
%\begin{figure}
%  \centering
%  \subfloat{\label{fig:mabs-p0.05}\includegraphics[width=0.8\textwidth]{../images/mabs-p005.png}}                
%  \\ \vspace{5mm}
%  \subfloat{\label{fig:mabs-p0.1}\includegraphics[width=0.8\textwidth]{../images/mabs-p01.png}}
%  \caption{MABS as a function of n}
%  \label{fig:mabs-fixed-p}
%\end{figure}

@@

\clearpage
\section{Calculating a Skew-Normal Approximation}
\label{app:calc-sn-approx}
